Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation\thanksref{footnoteinfo}

### 2020-08-26 main.tex
Fixed LCAO game to capture not knowing weights at time t, and consistent weights for all participants at the same time t. Wrote proof showing that if non-negligible adversary exists for LCAO, then the Joye-Libert scheme is not AO secure (which is proven to be the case) - referenced details about AO game and the Joye-Libert scheme that I think weren't made clear enough in it's description - need to update that next

\subsection{Paillier Encryption Scheme}
The Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} is an additively homomorphic encryption scheme which bases its security on the decisional composite residuosity assumption (DCRA) and meets the security notion of IND-CPA. Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $N=pq$. A generator $g$ is also required for encryption, which is often set to $g=N+1$ when $p$ and $q$ are of equal bit length \cite{}. The public key is defined by $(N, g)$ and secret key by $(p, q)$.

@@

\subsection{Joye-Libert Private Aggregation Scheme}
The Joye-Libert private aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data and meets the security notion of AO. Similarly to the Paillier scheme, it bases its security on the DCRA. A notable difference to a public-key encryption scheme is the need for a trusted party to perform an initial key generation and distribution step.

@@

\subsection{Linear-Combination Aggregator Oblivious Encryption} \label{subsec:lcao}
We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$. For the sake of readbility, we have ommited the time variable $t$ from values $\omega_j$ and $x_{i,j}$.

\begin{description}
    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the remaining user private keys $sk_i,\,1\leq i \leq n$.
    \item[$\mathsf{Enc}(pk_0, \omega)$] The aggregator and users can encrypt a weight $\omega$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(\omega)$.
    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m), x_{i,1},\dots,x_{i,m})$] At time $t$, user $i$ computes and obtains the encrypted linear combination $y_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ using its secret key $sk_i$.
    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y_1,\dots,y_n)$] At time $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}\omega_j$ using its private key $sk_0$.
\end{description}

@@

\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The three types of actions are:
    \begin{enumerate}
        \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ such that for any two chosen combine query tuples $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ and $(i',t',\mathcal{E}_{pk_0}(\omega_1'),\dots,\mathcal{E}_{pk_0}(\omega_m'),x_{i',1}',\dots,x_{i',m}')$ the following conditions hold:
        \begin{equation*}
            t = t' \implies \mathcal{E}_{pk_0}(\omega_j) = \mathcal{E}_{pk_0}(\omega_j'),\,1\leq j\leq m
        \end{equation*}
        and
        \begin{equation*}
            i = i' \wedge t = t' \implies x_{i,m} = x_{i',m}',\,1\leq j\leq m\,.
        \end{equation*}
        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{enumerate} 
    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $U \subseteq S$ where $S$ is the complete set of users for which no combine queries for time $t^*$ and no compromise queries are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})\,|\,i \in U\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,\mathcal{E}_{pk_0}(\omega_1'),\dots,\mathcal{E}_{pk_0}(\omega_m'),x_{i,1}',\dots,x_{i,m}')\,|\, i \in U\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in U$ (\textit{i.e.} the aggregator is compromised) and $U = S$, it is additionally required that
    \begin{equation*}
        \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}\omega_j = \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}'\omega_j'\,.
    \end{equation*}
    The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)\,|\,i\in U\rangle
    \end{equation*}
    if $b=0$, or 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}'\omega_j')\,|\,i\in U\rangle
    \end{equation*}
    otherwise.
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $U \subseteq S$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}

\begin{definition}
    An encryption scheme meets LCAO security if no probabilistic-time adversary has more than a negligible advantage in winning the above security game.
\end{definition}

@@

\section{Our Scheme}
Our scheme is based on the Paillier and Joye-Libert schemes introduced in Section \ref{sec:crypto_prelim}, and similarly bases its security on the DCRA. As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys. Below, we give definitions for the four algorithms comprising the linear-combination aggregation encryption scheme.

@@

    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m), x_{i,1},\dots,x_{i,m})$] The linear combination encryption step at time $t$ is computed as 
    \begin{equation}
        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,
    \end{equation}
    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
    \begin{equation*}
        \begin{split}
             y^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j} r^{N}_{j} \pmod{N^2} \\
            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j} r_{i}^{N} \pmod{N^2}\,,
        \end{split}
    \end{equation*}
    for some values $r_i,r_j \in \mathbb{Z}_N\,,1\leq j \leq m$.

    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y_1,\dots,y_n)$] Aggregation is computed as $y^{(t)} = \prod^n_{i=1}y^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and followed by Paillier decryption
    \begin{equation}
        \begin{split}
            \sum^{n}_{i=1}\sum^{m}_{j=1}&x^{(t)}_{i,j}\omega^{(t)}_j =\\
            &\frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,.
        \end{split}
    \end{equation}
    The correctness of aggregation can be seen from
    \begin{align*}
        y^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x_{i,j}\omega_j}r_i^N \pmod{N^2} \\
        \begin{split}
            &= H(t)^{\sum^n_{i=1}sk_i}\cdot \\
            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N \pmod{N^2}
        \end{split}\\
        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r'^N \pmod{N^2}\,,
    \end{align*}
    for some values $r_i,r' \in \mathbb{Z}_N,\,1\leq i \leq n$.
\end{description}

@@

\subsection{Proof}
To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights. From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme, and therefore meet security notion IND-CPA. We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{} instead.

To show our scheme meets the security notion of LCAO, we prove by contrapositive that given a polynomial-time adversary $\mathcal{A}$ with non-negligible advantage $\mathsf{Adv}^{LCAO}(\mathcal{A})$ against a challenger using our scheme (\textit{i.e.} if we assume our scheme is not LCAO secure) we can construct an adversary $\mathcal{A}'$ with non-negligible advantage $\mathsf{Adv}^{AO}(\mathcal{A}')$ against a challenger using the Joye-Libert private aggregation scheme (\textit{i.e.} then the Joye-Libert scheme is not AO secure). As this is a contradiction to the Joye-Libert AO proof in \cite{}, our scheme must meet LCAO security.
\begin{pf}
    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}. The following is a construction of adversary $\mathcal{A}'$ playing the AO game from Appendix \ref{app:ao} against a challenger $\mathcal{C}$.
    \begin{description}
        \item[$\mathsf{Setup}$] $\mathcal{A}'$ receives $N$ and $H$ as public parameters from $\mathcal{C}$, and generates a new key with same size $N'=pq$ and creates aggregator public and private keys $pk_0$, $sk_0$, chooses an $m>1$, and gives $H$, $m$, and $pk_0$ to $\mathcal{A}$
        \item[$\mathsf{CombEnc}$] When $\mathcal{A}$ makes combine encryption queries $(i, t, \mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m), x_{i,1},\dots,x_{i,m})$, $\mathcal{A}'$ uses $sk_0$ to decrypt weights $\omega_1,\dots,\omega_m$ and makes an $\mathsf{Enc}(i, t, \sum^m_{j=1}x_{i,j}\omega_j)$ query to $\mathcal{C}$. The received response is of the form $(N+1)^{\sum^m_{j=1}x_{i,j}\omega_j}H(t)^{sk_i}$, from which $H(t)^{sk_i}$ is recovered by
        \begin{equation*}
            H(t)^{sk_i} = (N+1)^{\sum^m_{j=1}x_{i,j}\omega_j}H(t)^{sk_i}((N+1)^{\sum^m_{j=1}x_{i,j}})^{-1} \pmod{N^2}
        \end{equation*}
        where $^-1$ denotes the modular inverse. 
    \end{description}

    Note that decryption and encryption are polynomial in security parameter and therefore\dots
\end{pf}

@@

\section{Results}
Decide on what kind of simulations and which plots to make. run times would be nice this time around

Time results can be captured in one graph. Y-axis is time, X-axis is the number of sensors, each line (different colour) will show how the runtime changes as sensors are increased for different Paillier bit-sizes (at least 3: 512, 1024, 2048). Every data point should be the average over some X number of simulations.

>>>>

\subsection{Paillier Encryption Scheme} \label{subsec:paillier_scheme}
The Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} is an additively homomorphic encryption scheme which bases its security on the decisional composite residuosity assumption (DCRA) and meets the security notion of IND-CPA. Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $N=pq$. A generator $g$ is also required for encryption, which is often set to $g=N+1$ when $p$ and $q$ are of equal bit length \cite{}. The public key is defined by $(N, g)$ and secret key by $(p, q)$.

@@

\subsection{Joye-Libert Private Aggregation Scheme} \label{subsec:joye_libert_scheme}
The Joye-Libert private aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data and meets the security notion of AO. Similarly to the Paillier scheme, it bases its security on the DCRA. A notable difference to a public-key encryption scheme is the need for a trusted party to perform an initial key generation and distribution step.

@@

\subsection{Linear-Combination Aggregator Oblivious Encryption} \label{subsec:lcao}
We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$, defined as

\begin{description}
    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the remaining user private keys $sk_i,\,1\leq i \leq n$.
    \item[$\mathsf{Enc}(pk_0, \omega)$] The aggregator and users can encrypt a weight $\omega$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(\omega)$.
    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] At time $t$, user $i$ computes and obtains the encrypted linear combination $y^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At time $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
\end{description}

@@

\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{enumerate}
        \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
        \item \textit{Weight Queries:} The attacker chooses a time $t$ and receives the weights for that time encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies x^{(t)}_{i,m} = x^{\prime(t')}_{i',m},\,1\leq j\leq m\,.
        \end{equation*}
        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{enumerate} 
    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen time $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in U\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}

\begin{definition}
    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter, has more than a negligible advantage in winning the above security game. Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
\end{definition}

@@

\section{Our Scheme} \label{sec:our_scheme}
Our scheme is based on the Paillier and Joye-Libert schemes introduced in Section \ref{sec:crypto_prelim}, and similarly bases its security on the DCRA. As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys. Below, we give definitions for the four algorithms comprising the linear-combination aggregation encryption scheme.

@@

    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] The linear combination encryption step at time $t$ is computed as 
    \begin{equation}
        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,
    \end{equation}
    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
    \begin{equation*}
        \begin{split}
             y^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j} r^{N}_{j} \pmod{N^2} \\
            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j} r_{i}^{N} \pmod{N^2}\,,
        \end{split}
    \end{equation*}
    for some values $r_i,r_j \in \mathbb{Z}_N\,,1\leq j \leq m$.

    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] Aggregation is computed as $y^{(t)} = \prod^n_{i=1}y^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and is followed by Paillier decryption
    \begin{equation}
        \begin{split}
            \sum^{n}_{i=1}\sum^{m}_{j=1}&x^{(t)}_{i,j}\omega^{(t)}_j =\\
            &\frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,.
        \end{split}
    \end{equation}
    The correctness of aggregation can be seen from
    \begin{align*}
        y^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x_{i,j}\omega_j}r_i^N \pmod{N^2} \\
        \begin{split}
            &= H(t)^{\sum^n_{i=1}sk_i}\cdot \\
            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N \pmod{N^2}
        \end{split}\\
        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r'^N \pmod{N^2}\,,
    \end{align*}
    for some values $r_i,r' \in \mathbb{Z}_N,\,1\leq i \leq n$.
\end{description}

@@

\subsection{Proof}
To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights. From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme, and therefore meet security notion IND-CPA. We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} instead.

To show our scheme meets the security notion of LCAO, we prove by contrapositive that for an adversary $\mathcal{A}$ playing against a challenger using \textit{our scheme}, we can create an adversary $\mathcal{A}'$ playing against a challenger using the \textit{Joye-Libert scheme}, such that
\begin{equation*}
    \mathsf{Adv}^{LCAO}(\mathcal{A}) > \eta_1(\kappa) \implies \mathsf{Adv}^{AO}(\mathcal{A}') > \eta_2(\kappa)\,,
\end{equation*}
for some negligible functions $\eta_1$ and $\eta_2$. (\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) This is a contradiction to the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, and will thus conclude our proof.
\begin{pf}
    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}. The following is a construction of an adversary $\mathcal{A}'$ playing the AO game in Appendix \ref{app:ao} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme from Section \ref{subsec:joye_libert_scheme}.
    \begin{description}
        \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
        \item[Queries] Handle queries from $\mathcal{A}$:
        \begin{description}
            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $r_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions 
            \begin{equation*}
                (N+1)^{(\omega^{(t)}_{j})}r_j^N\pmod{N^2},\,1\leq j\leq m
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for time $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$. The received response is of the form $(N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $r^N$ for a random $r \in \mathbb{Z}_N$ and return 
            \begin{equation*}
                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N H(t)^{sk_i} \pmod{N^2}
            \end{equation*}
            to $\mathcal{A}$.
            \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
        \end{description}
        \item[Challenge] When $\mathcal{A}$ submits challenge series
        \begin{equation*}
            \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
        \end{equation*}
        and
        \begin{equation*}
            \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
        \end{equation*}
        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for time $t^*$ and submit AO challenge series
        \begin{equation*}
            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle
        \end{equation*}
        and
        \begin{equation*}
            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle\,,
        \end{equation*}
        to $\mathcal{C}$. The received response if of the form 
        \begin{equation*}
            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,|\,i\in U\rangle\,,
        \end{equation*}
        for an unkonwn $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return
        \begin{equation*}
            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle\,,
        \end{equation*}
        to $\mathcal{A}$.
        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to $\mathcal{C}$.
    \end{description}

    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ behaves identically to our scheme described in Section \ref{sec:our_scheme}. Since $\mathcal{A}'$ runs in polynomial-time to security parameter when $\mathcal{A}$ does, and no non-neglibile advantage adversary to $\mathcal{C}$ exists \cite{joyeScalableSchemePrivacyPreserving2013}, we conclude that no non-negligible advantage adversary $\mathcal{A}$ exists. That is, there exists a negligible function $\eta$, such that
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \leq \eta(\kappa)
    \end{equation*}
    for security parameter $\kappa$. \qed
\end{pf}

@@

\section{Results}
Time results can be captured in one graph. Y-axis is time, X-axis is the number of sensors, each line (different colour) will show how the runtime changes as sensors are increased for different Paillier bit-sizes (at least 3: 512, 1024, 2048). Every data point should be the average over some X number of simulations.
